The Noisy Work of Uncertainty Visualisation Research: A Review

### 2024-05-13 paper.qmd
minor edits + knitted paper

This leads us to wonder *how* signal suppression should be tested.

@@

## Mistakes made when we misunderstand uncertainty visualisation
In the previous section, we highlighted several problematic experimental designs or pieces of research that were the result of misunderstandings around the definition of uncertainty. Here, we will discuss the issues that arise due to a misunderstanding of "uncertainty visualisation". The two primary problems are the regular comparisons of mathematically incomparable plots, and reproducing results that are already widely understood in the larger information visualisation literature.

>>>>

{{< pagebreak >}}

**The following sections are in the middle of being reorganized and rewritten so it will not flow on from the previous sections**

{{< pagebreak >}}

@@
